Study of Higgs plus single top production using events with a same sign dimuon at the Large Hadron Collider

### 2019-12-05 presentacion_hiram/presentacion-tesis.tex
n

\documentclass[11pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{array}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{listings}
\usepackage{alltt}
\usepackage{mathtools}
\usepackage[makeroom]{cancel}
%\usetheme{Frankfurt}
\usepackage{tikz} 
\usepackage{pgfplots}
\usetikzlibrary{patterns}
\usetikzlibrary{plotmarks}
\titlegraphic{\vspace{8cm}}% to push the other text to the top
\addtobeamertemplate{navigation symbols}{}{%
	\usebeamerfont{footline}%
	\usebeamercolor[fg]{footline}%
	\hspace{1em}%
	\insertframenumber/\inserttotalframenumber
	\setbeamercolor{footline}{fg=blue}
	\setbeamerfont{footline}{series=\bfseries}
}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\newcommand\Fontvi{\fontsize{4}{7.2}\selectfont}

 \author{\tiny
   L.F. Hiram Ernesto Dami\'an\\
   \vspace{5px}
   Director:\\
   \vspace{5px}
   Jos\'e Feliciano Ben\'itez Rubio\\
   \vspace{5px}
   Maestr\'ia en Ciencias (F\'isica)\\
   \vspace{5px}
   Departamento de Investigacion en F\'isica }
 \title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
 %\subtitle{}
 \logo{\includegraphics[scale=0.1]{unison-logo.png}}
 \newcommand{\nologo}{\setbeamertemplate{logo}{}}
 \institute{Universidad de Sonora}
 \date{\small November 25$^{th}$ 2019}
 %\subject{}
 \newcommand{\subf}[2]{%
   {\small\begin{tabular}[t]{@{}c@{}}
     #1\\#2
   \end{tabular}}%
 }
 %\setbeamercovered{transparent}
 %\setbeamertemplate{navigation symbols}{}

@@

\begin{frame}
\tiny
\tableofcontents
\end{frame}

@@

\begin{frame}
\subsection{Higgs mechanism}
\frametitle{Electroweak SM Lagrangian}
Higgs lagrangian 
\begin{align}
\mathcal{L}_{\text{Higgs}}=(D_\mu \Phi)^\dagger (D^\mu \Phi)-V(\Phi^\dagger \Phi)
\end{align}

@@

\begin{frame}
\frametitle{Cross section}
\begin{itemize}
\item Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
\begin{align}
N_R=\sigma \text{L}
\end{align}
%\item Experimentally
%\begin{align}
%d\sigma=\frac{\text{number of particles scattered into solid angle} \Delta\Omega}{\text{(number of particles incident)(scattering centers/area)}}
%\end{align}
\item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{-2}$ 
\item The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.\\
L is called luminosity and it is measured in cm$^{-2}$s$^{-1}$.\cite{6}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Higgs production Cross section}
\begin{table}
	\caption*{Higgs boson production cross sections  in pp collisions for $\sqrt{s}=13$TeV  (in
		pico barn).Integrated luminosity of 35.9 fb$^{-1}$ for Run 2\footnotemark}
	\begin{tabular}{|c|c|c|}
		\hline
		Production mechanism &
		$\sigma$ (picobarns pb)
		&Number of events \\
		\hline
		ggF &
		48.93 &
		1756587\\
		\hline
		VBF &
		3.78&
		135702\\
		\hline
		WH & 1.35 & 48465\\
		\hline
		ZH &0.88 & 31592\\
		\hline
		t$\bar{t}$H &
		0.50&
		18183\\
		\hline
		$tH$ &
		0.074&
		2665\\
		\hline
	\end{tabular}
\end{table}

\footnotetext[1]{\tiny{Data taken from The cern collaborarion “Higgs Physics the HL-LHC and HE-LHC” 2019, CERN-LPCC-2018-04}}

\begin{frame}
\frametitle{Branching ratio}
\small{In particle physics, the branching ratio for a decay process is the ratio of the number of particles which decay via a specific decay mode with respect to the total number of particles which decay via all decay modes. \footnotemark.}
\begin{align}
\text{BR} =\frac{\Gamma_i}{\sum_{i}\Gamma_i}
\end{align}
\small{Where $\Gamma=\sum_i\Gamma_i$ is the total decay width (sum of all partial widths) of the particle and is related to lifetime of the particle: $\Gamma=1/\tau$.
Since the dimension of $\Gamma$ is the inverse of time, in our system of natural units, it is measured in inverse seconds} .%it has the same dimension as mass (or energy).}
\footnote[0]{\tiny{Cleaves H.J. (2011) Branching Ratio. In: Gargaud M. et al. (eds) Encyclopedia of Astrobiology. Springer, Berlin, Heidelberg} }
\end{frame}

@@

%\begin{frame}
%\section{Statistical analysis}
%\frametitle{Fitting}
%	\begin{center}
%	\begin{figure}
%		\includegraphics[width=10.5cm]{figures/fit-box.png}
%		\caption*{}
		%\caption*{}
%	\end{figure}
%\end{center}
%\end{frame}

@@

\begin{frame}
\section{Results}
\frametitle{Results}
	\begin{table}[ht!]
		\centering
		\caption*{Postfit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
		\begin{tabular}{ccc}
			\hline
			Process & SM & $k_{t}$=-1 \\
			\hline
			$t\bar{t}W$ & 68$\pm$8.9& 68 $\pm$8.9 \\
			$t\bar{t}Z$ & 25.9$\pm$3.8&25.9$\pm$3.8\\
			$WZ$ & 15.1$\pm$7.4& 15.1$\pm$7.4\\
			Rares & 20.8$\pm$4.8& 20.8$\pm$4.8 \\
			Fakes & 80.9$\pm$9.0& 80.9$\pm$8.9 \\
			$t\bar{t}H$ & 24.2$\pm$2.0 & 24.2$\pm$2.0 \\
			\hline
			$tH$& 2.1$\pm$16.5 &26.2$\pm$13.1 
		\end{tabular}
		\label{table1}
	\end{table}
 Prefit uncertainty is statistical only. Postfit uncertainty is statistical + systematic.
\end{frame}

\begin{frame}
\frametitle{Results}
\framesubtitle{Likelihood scan}
{\small
	\begin{itemize}
\item Due to the large background, the signal strength for the Asimov data with 35.9 fb$^{-1}$ is consistent with zero.
Therefore, we estimate an upper limit on the signal strength at 95$\%$ confidence level.
\item We can define the likelihood ratio
\begin{align}
\lambda(\mu,\alpha)=\frac{L(\mu,\alpha)}{L(\hat{\mu},\hat{\alpha})}
\end{align}
Where $\hat{\alpha}$ and $\hat{\mu}$ are the parameters obtained in the previous section which correspond to the minimal of the NLL.
\item To determine an upper limit on the strength parameter $\mu$, we use the following statistical test
\begin{align}
q(\mu,\alpha)= -2\ln{\lambda} 
\end{align}
\item High values of $q$ represent greater incompatibility between the data and the fit model.
$q$ is a random variable with a $\chi^2$ distribution.
\end{itemize}
}
\end{frame}

@@

\begin{frame}
\frametitle{Conclusions}
\begin{itemize}
\item The results of the analysis for the SM case indicates that it is impossible to give an evidence of a Higgs boson using same sign dimuon channel in the $tH$ process due to large statistical uncertainty.
\item For the SM scenario the limit in the signal strength for 3000 fb$^{-1}$ is 4.3 at 95$\%$ of confidence level.
\item For the inverted coupling scenario ($k_t$ =-1), the uncertainty after the fit was around 50$\%$ for a luminosity of 35.9 fb$^{-1}$. This is due to the larger expected number of signal events.
\item For the modified $k_t$=-1 model for 3000 fb$^{-1}$, it is possible to measure a hypothetical signal with 10$\%$ of uncertainty.
\item It is required a new analysis that includes more channels such as three leptons in the final state for improve the sensibility of the signal.
\end{itemize}
\end{frame}

@@

\begin{frame}
\section{Supportive slides}
\huge{Back up}
\end{frame}

>>>>

\documentclass[11pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{array}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{listings}
\usepackage{alltt}
\usepackage{mathtools}
\usepackage[makeroom]{cancel}
\usetheme{Rochester}
%\usecolortheme{dove}
%\usetheme{Pittsburgh}
\usepackage{tikz} 
\usepackage{pgfplots}
\usetikzlibrary{patterns}
\usetikzlibrary{plotmarks}
\titlegraphic{\vspace{8cm}}% to push the other text to the top
\addtobeamertemplate{navigation symbols}{}{%
	\usebeamerfont{footline}%
	\usebeamercolor[fg]{footline}%
	\hspace{1em}%
	\insertframenumber/\inserttotalframenumber
	\setbeamercolor{footline}{fg=blue}
	\setbeamerfont{footline}{series=\bfseries}
}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\newcommand\Fontvi{\fontsize{4}{7.2}\selectfont}

 \author{\scriptsize
 	Universidad de Sonora\\
 	\vspace{5px}
 	Divisi\'on de Ciencias Exactas y Naturales\\
 	\vspace{5px}
 	Departamento de Investigaci\'on en F\'isica\\
 	   \vspace{5px}
   L.F. Hiram Ernesto Dami\'an\\
   Defensa de tesis para obtener el grado de \\
      Maestr\'ia en Ciencias (F\'isica)\\
         \vspace{5px}
   Director:\\
   \vspace{5px}
   Jos\'e Feliciano Ben\'itez Rubio\\
   \vspace{5px}}
 \title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
 %\subtitle{}
 \logo{\includegraphics[scale=0.1]{unison-logo.png}}
 \newcommand{\nologo}{\setbeamertemplate{logo}{}}
 \date{\small November 25$^{th}$ 2019}
 %\subject{}
 \newcommand{\subf}[2]{%
   {\small\begin{tabular}[t]{@{}c@{}}
     #1\\#2
   \end{tabular}}%
 }
 %\setbeamercovered{transparent}
 %\setbeamertemplate{navigation symbols}{}

@@

\begin{frame}
	\frametitle{Table of contents}
\tiny
\tableofcontents
\end{frame}

@@

\begin{frame}
\subsection{Electroweak SM Lagrangian}
\frametitle{Electroweak SM Lagrangian}
Higgs lagrangian 
\begin{align}
\mathcal{L}_{\text{Higgs}}=(D_\mu \Phi)^\dagger (D^\mu \Phi)-V(\Phi^\dagger \Phi)
\end{align}

@@

\begin{frame}
\frametitle{Cross section}
\begin{itemize}
	\item The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.
	\begin{align}
	N_R=\sigma \text{L}
	\end{align}
\item Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
%\item Experimentally
%\begin{align}
%d\sigma=\frac{\text{number of particles scattered into solid angle} \Delta\Omega}{\text{(number of particles incident)(scattering centers/area)}}
%\end{align}
\item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{-2}$

\item L is called luminosity and it is measured in cm$^{-2}$s$^{-1}$.\cite{6}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Higgs production Cross section}
\begin{table}
	\caption*{Higgs boson production cross sections  in pp collisions for $\sqrt{s}=13$TeV  (in
		pico barn).Integrated luminosity of 35.9 fb$^{-1}$ for Run 2\footnotemark}
	\begin{tabular}{|c|c|c|}
		\hline
		Production mechanism &
		$\sigma$ (picobarns pb)
		&Number of events \\
		\hline
		ggF &
		48.93 &
		1756587\\
		\hline
		VBF &
		3.78&
		135702\\
		\hline
		WH & 1.35 & 48465\\
		\hline
		ZH &0.88 & 31592\\
		\hline
		t$\bar{t}$H &
		0.50&
		18183\\
		\hline
		$tH$ &
		0.074&
		2665\\
		\hline
	\end{tabular}
\end{table}
\footnotetext[1]{\tiny{Data taken from The cern collaborarion “Higgs Physics the HL-LHC and HE-LHC” 2019, CERN-LPCC-2018-04}}
\end{frame}

\begin{frame}
\frametitle{Branching ratio}
\small{In particle physics, the branching ratio for a decay process is the ratio of the number of particles which decay via a specific decay mode with respect to the total number of particles which decay via all decay modes.}
\begin{align}
\text{BR} =\frac{\Gamma_i}{\sum_{i}\Gamma_i}
\end{align}
\small{Where $\Gamma=\sum_i\Gamma_i$ is the total decay width (sum of all partial widths) of the particle and is related to lifetime of the particle: $\Gamma=1/\tau$.}
%it has the same dimension as mass (or energy).}
\end{frame}

@@

%\begin{frame}
\section{Statistical analysis}
%\frametitle{Fitting}
%	\begin{center}
%	\begin{figure}
%		\includegraphics[width=10.5cm]{figures/fit-box.png}
%		\caption*{}
		%\caption*{}
%	\end{figure}
%\end{center}
%\end{frame}

@@

\begin{frame}
\frametitle{Results}
	\begin{table}[ht!]
		\centering
		\caption*{Postfit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
		\begin{tabular}{ccc}
			\hline
			Process & SM & $k_{t}$=-1 \\
			\hline
			$t\bar{t}W$ & 68$\pm$8.9& 68 $\pm$8.9 \\
			$t\bar{t}Z$ & 25.9$\pm$3.8&25.9$\pm$3.8\\
			$WZ$ & 15.1$\pm$7.4& 15.1$\pm$7.4\\
			Rares & 20.8$\pm$4.8& 20.8$\pm$4.8 \\
			Fakes & 80.9$\pm$9.0& 80.9$\pm$8.9 \\
			$t\bar{t}H$ & 24.2$\pm$2.0 & 24.2$\pm$2.0 \\
			\hline
			$tH$& 2.1$\pm$16.5 &26.2$\pm$13.1 
		\end{tabular}
		\label{table1}
	\end{table}
 Prefit uncertainty is statistical only. Postfit uncertainty is statistical + systematic.
\end{frame}

\begin{frame}
	\subsection{Extrapolation to higher luminosity}
\frametitle{Results}
\framesubtitle{Likelihood scan}
{\small
	\begin{itemize}
\item Due to the large background, the signal strength for the Asimov data with 35.9 fb$^{-1}$ is consistent with zero.
Therefore, we estimate an upper limit on the signal strength at 95$\%$ confidence level.
\item We can define the likelihood ratio
\begin{align}
\lambda(\mu,\alpha)=\frac{L(\mu,\alpha)}{L(\hat{\mu},\hat{\alpha})}
\end{align}
Where $\hat{\alpha}$ and $\hat{\mu}$ are the parameters obtained in the previous section which correspond to the minimal of the NLL.
\item To determine an upper limit on the strength parameter $\mu$, we use the following statistical test
\begin{align}
q(\mu,\alpha)= -2\ln{\lambda} 
\end{align}
\item High values of $q$ represent greater incompatibility between the data and the fit model.
$q$ is a random variable with a $\chi^2$ distribution.
\end{itemize}
}
\end{frame}

@@

\begin{frame}
	\section{Conclusions}
\frametitle{Conclusions}
\begin{itemize}
\item The results of the analysis for the SM case indicates that it is impossible to give an evidence of a Higgs boson using same sign dimuon channel in the $tH$ process due to large statistical uncertainty.
\item For the SM scenario the limit in the signal strength for 3000 fb$^{-1}$ is 4.3 at 95$\%$ of confidence level.
\item For the inverted coupling scenario ($k_t$ =-1), the uncertainty after the fit was around 50$\%$ for a luminosity of 35.9 fb$^{-1}$. This is due to the larger expected number of signal events.
\item For the modified $k_t$=-1 model for 3000 fb$^{-1}$, it is possible to measure a hypothetical signal with 10$\%$ of uncertainty.
\item It is required a new analysis that includes more channels such as three leptons in the final state for improve the sensibility of the signal.
\end{itemize}
\end{frame}

@@

%\begin{frame}
%\section{Supportive slides}
%\huge{Back up}
%\end{frame}
